### 2018-10-16 VV556/HW4/submission.tex
4.2-2 basically ok

\section{Exercise4.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				The orthogonal property is justified as
				\begin{equation}
					\int_{0}^{\pi} (\frac{1}{\sqrt{\pi}})^2 dx = \frac{1}{\pi} \int_{0}^{\pi} dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \frac{1}{\sqrt{\pi}} \sqrt{\frac{2}{\pi}}cos(nx) dx = 0
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \sqrt{\frac{2}{\pi}}cos(nx) \sqrt{\frac{2}{\pi}}cos(mx) dx = \frac{2}{\pi} \int_{0}^{\pi} cos(nx) cos(mx) dx = 0
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}

			\end{proof}

>>>>

\section{Exercise4.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				The orthogonal property is justified as
				\begin{equation}
					\int_{0}^{\pi} (\frac{1}{\sqrt{\pi}})^2 dx = \frac{1}{\pi} \int_{0}^{\pi} dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = \frac{1}{\pi} \int_{0}^{\pi} (cos(2nx) + 1) dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \frac{1}{\sqrt{\pi}} \sqrt{\frac{2}{\pi}}cos(nx) dx = 0
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \sqrt{\frac{2}{\pi}}cos(nx) \sqrt{\frac{2}{\pi}}cos(mx) dx = \frac{2}{\pi} \int_{0}^{\pi} cos(nx) cos(mx) dx = 0
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				It's trival to show both $K=0$ and $K=1$ are valid, and $K=2$ is also justified as
				\begin{equation}
					cos^2(x) = \frac{1+cos(2x)}{2}
				\end{equation}
				Assume the proposition is also valid for $K=n$, that means
				\begin{equation}
					span\{1, cos(x), cos(2x), ... cos(nx)\} = span\{1, cos(x), cos^2(x), ... cos^n(x)\}
				\end{equation}
				which indicates that $\exists a_k$ and $b_k (k=0, 1, ..., n)$ s.t. 
				\begin{equation}
					cos^n(x) = \sum_{k=0}^{n} a^{(n)}_k \cdot cos(kx)
				\end{equation}
				\begin{equation}
					cos(nx) = \sum_{k=0}^{n} b^{(n)}_k \cdot cos^k(x)
				\end{equation}
				When $K = n+1$, the proposition is still valid as
				\begin{equation}
					\begin{aligned}
						cos^{n+1}(x) & = cos(x) \sum_{k=0}^{n} a_k cos(kx)\\
									 & = a_0 cos(x) + cos(x) \sum_{k=1}^{n-1} a_k cos(kx) + a_n cos(x) cos(nx)\\
									 & = a_0 cos(x) + \sum_{k=1}^{n-1} \frac{a_k}{2} [cos(k-1)x + cos(k+1)x] + \frac{a_n}{2} [cos(n-1)x + cos(n+1)x]\\
									 & = \frac{a_1}{2} + (a_0 + \frac{a_2}{2}) cos(x) + \sum_{k=2}^{n-1}\frac{a_{k-1} + a_{k+1}}{2} cos(kx) + \frac{a_n}{2} cos(n+1)x
					\end{aligned}
				\end{equation}
				and
				\begin{equation}
					\begin{aligned}
						cos(n+1)x & = 2 cos(nx)cos(x) - cos(n-1)x\\
								  & = 2 cos(x)\sum_{k=0}^{n} b^{(n)}_k cos^k(x) - \sum_{k=0}^{n-1} b^{(n-1)}_k cos^k(x)\\
								  & = -b^{(n-1)}_0 + \sum_{k=0}^{n-1} (2b^{(n)}_k - b^{(n-1)}_k) cos^{k+1}(x) + 2b^{(n)}_k cos^{n+1}(x)
					\end{aligned}
				\end{equation}
			\end{proof}
		\item
